---
title: "OPTIMA Cost-Effectiveness Analysis - Deterministic Sensitivity Analysis"
author: "Benjamin Enns"
date: "2/4/2022"
output: html_document
---

```{r, echo=FALSE, eval=TRUE, warning=FALSE, cache=FALSE, message=FALSE}
library(dplyr)    # to manipulate data
library(reshape2) # to transform data
library(ggplot2)  # for nice looking plots
library(tidyverse)
library(data.table)
library(formattable)
library(tidyr)
library(RColorBrewer)
```

```{r, echo=F, eval=T, warning=FALSE, cache=F, message=F}
improvement_formatter <- formatter("span", 
                                   style = x ~ style(font.weight = "bold", 
                                                     color = ifelse(x > 0, customGreen, ifelse(x < 0, customRed, "black"))), 
                                   x ~ icontext(ifelse(x>0, "arrow-up", "arrow-down"), x))

# set colours
customGreen0 = "#DeF7E9"
customGreen = "#71CA97"
customRed = "#ff7f7f"
overdose_nonfatal_palette <- brewer.pal(3,"PuOr")
overdose_fatal_palette <- brewer.pal(3,"PuOr")
qaly_palette <- brewer.pal(3,"PuOr")
crime_costs_palette <- brewer.pal(3,"BrBG")
```

# DSA Results
<p>&nbsp;</p>
## QALY weights
<p>&nbsp;</p>
### Modified Model Specification
<p>&nbsp;</p>
```{r, echo=F, eval=T, warning=FALSE, cache=F, message=F}
load(file = "outputs/DSA/Modified Model Specification/ftable_qalys_out.RData")
ftable_qalys_out
```

<p>&nbsp;</p>
### Trial Specification
<p>&nbsp;</p>
```{r, echo=F, eval=T, warning=FALSE, cache=F, message=F}
load(file = "outputs/DSA/Trial Specification/ftable_qalys_TS_out.RData")
ftable_qalys_TS_out
```

<p>&nbsp;</p>
## Crime costs
<p>&nbsp;</p>
### Modified Model Specification
<p>&nbsp;</p>
```{r, echo=F, eval=T, warning=FALSE, cache=F, message=F}
load(file = "outputs/DSA/Modified Model Specification/ftable_crime_costs_out.RData")
ftable_crime_costs_out
```

<p>&nbsp;</p>
### Trial Specification
<p>&nbsp;</p>
```{r, echo=F, eval=T, warning=FALSE, cache=F, message=F}
load(file = "outputs/DSA/Trial Specification/ftable_crime_costs_TS_out.RData")
ftable_crime_costs_TS_out
```

<p>&nbsp;</p>
## Nonfatal Overdose
<p>&nbsp;</p>
### Modified Model Specification
<p>&nbsp;</p>
```{r, echo=F, eval=T, warning=FALSE, cache=F, message=F}
load(file = "outputs/DSA/Modified Model Specification/ftable_overdose_nonfatal_qalys_MMS_out.RData")
ftable_overdose_nonfatal_qalys_MMS_out
```

<p>&nbsp;</p>
```{r, echo=F, eval=T, warning=FALSE, cache=F, message=F}
load(file = "outputs/DSA/Modified Model Specification/ftable_overdose_nonfatal_costs_MMS_out.RData")
ftable_overdose_nonfatal_costs_MMS_out
```

<p>&nbsp;</p>
### Trial Specification
<p>&nbsp;</p>
```{r, echo=F, eval=T, warning=FALSE, cache=F, message=F}
load(file = "outputs/DSA/Trial Specification/ftable_overdose_nonfatal_qalys_TS_out.RData")
ftable_overdose_nonfatal_qalys_TS_out
```

<p>&nbsp;</p>
```{r, echo=F, eval=T, warning=FALSE, cache=F, message=F}
load(file = "outputs/DSA/Trial Specification/ftable_overdose_nonfatal_costs_TS_out.RData")
ftable_overdose_nonfatal_costs_TS_out
```

<p>&nbsp;</p>
## Fatal Overdose
<p>&nbsp;</p>
### Modified Model Specification
<p>&nbsp;</p>
```{r, echo=F, eval=T, warning=FALSE, cache=F, message=F}
load(file = "outputs/DSA/Modified Model Specification/ftable_overdose_fatal_qalys_MMS_out.RData")
ftable_overdose_fatal_qalys_MMS_out
```

<p>&nbsp;</p>
```{r, echo=F, eval=T, warning=FALSE, cache=F, message=F}
load(file = "outputs/DSA/Modified Model Specification/ftable_overdose_fatal_costs_MMS_out.RData")
ftable_overdose_fatal_costs_MMS_out
```

<p>&nbsp;</p>
### Trial Specification
<p>&nbsp;</p>
```{r, echo=F, eval=T, warning=FALSE, cache=F, message=F}
load(file = "outputs/DSA/Trial Specification/ftable_overdose_fatal_qalys_TS_out.RData")
ftable_overdose_fatal_qalys_TS_out
```

<p>&nbsp;</p>
```{r, echo=F, eval=T, warning=FALSE, cache=F, message=F}
load(file = "outputs/DSA/Trial Specification/ftable_overdose_fatal_costs_TS_out.RData")
ftable_overdose_fatal_costs_TS_out
```